---
title: "Recruitment Report"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    logo: www/isaricwhite.png
    css: www/styles.css
---

```{r render_setup, include = FALSE, echo = FALSE, message = FALSE}
library(rmarkdown)
library(tidyverse)
library(ggsci)
library(finalfit)
library(lubridate)
library(flexdashboard)
library(DT)

today_date = lubridate::today()

#generate data
source("07_source_data.R")
gc()

topline = topline %>% 
  distinct(subjid, .keep_all = T)

topline = topline %>% 
  mutate(tier_entered = ifelse(tiers_faorres___1 == 'Checked', 'Tier 0', NA),
         tier_entered = ifelse(tiers_faorres___2 == 'Checked', 'Tier 1', tier_entered),
         tier_entered = ifelse(tiers_faorres___3 == 'Checked', 'Tier 2', tier_entered),
         tier_entered = ifelse(is.na(tier_entered), 'Missing', tier_entered) %>% factor() %>% 
                                 fct_relevel('Tier 0', 'Tier 1', 'Tier 2', 'Missing')) %>% 
  mutate(place_name = as.character(place_name)) %>% 
  mutate(city = as.character(city)) %>%
  mutate(place_name = ifelse(place_name == 'Cardiff and Vale University Health Board', 'University Hospital Of Wales', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Chelsea and Westminster Hospital NHS, 369 Fulham Rd, London', 'Chelsea And Westminster Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Cheshire and Wirral Partnership NHSFT', 'Countess Of Chester Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Wirral University Teaching Hospital NHFT', 'Arrowe Park Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Royal United Hospitals Bath NHSFT', 'Royal United Hospitals', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Basildon and Thurrock University Hospitals NHS', 'Basildon University Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'The Queen Elizabeth Hospital Kings Lynn NHS Foundation Trust', 'The Queen Elizabeth Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Imperial College Healthcare NHS Trust', 'St Mary’s Hospital (Hq)', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'St Mary’s Hospital (Hq)', 'St Mary’s Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Pinderfields', 'Pinderfields Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Maidstone and Tunbridge Wells NHS Trust', 'Tunbridge Wells Hospital At Pembury', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Mid and South Essex University Hospitals Group', 'Southend Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'University Hospital Southampton NHS Foundation Trust', 'Southampton General Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'NUH Nottingham University Hosptial', 'Queen’s Medical Centre Campus', place_name)) %>% 
  mutate(place_name = ifelse(place_name == "Nottingham University Hospitals NHS Trust - Queen's Medical Centre Campus", 'Queen’s Medical Centre Campus', place_name))%>%
  mutate(place_name = ifelse(place_name == 'Nottingham University Hospitals Nhs Trust - City Campus', 'Nottingham City Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Diana', 'Diana, Princess of Wales Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'University College London Hospitals NHSFT', 'Royal Free Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'East Sussex Healthcare NHS Trust', 'Conquest Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'Calderdale and Huddersfield NHS Trust', 'Huddersfield Royal Infirmary', place_name)) %>% 
  mutate(city = ifelse(city == 'Bolsover', 'Chesterfield', city)) %>% 
  mutate(place_name = ifelse(place_name == 'Queen Elizabeth University Hospital, Glasgow', 'Queen Elizabeth University Hospital', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'University Hospital Monklands Airdrie', 'University Hospital Monklands', place_name)) %>% 
  mutate(place_name = ifelse(place_name == 'North West Boroughs Healthcare NHSFT', 'Warrington Hospital', place_name)) %>% 
  mutate(place_name = gsub('Nhs', 'NHS', place_name))
```

UK
=====================================
    
Row
-------------------------------------
    
### Patients in ISARIC 4C-UK (at time of last update)
    
```{r, fig.width = 8}
pts_in_uk = topline %>% 
  filter(!is.na(country)) %>% 
  group_by(country) %>% 
  summarise(count_recruited = n()) %>% 
  ggplot(aes(x = country, y = count_recruited, label = count_recruited)) + geom_bar(aes(fill = country), width = 0.5, stat = 'identity') + 
  xlab('Country') + geom_label() + scale_fill_lancet(name = 'Nation') + theme_classic(14) + ylab('Number of Patients')

pts_in_uk 

rm(pts_in_uk)
```
 
     
### Recruitment rate by Country
    
```{r, fig.width = 8}
topline_by_country = topline %>% 
  filter(!is.na(country)) %>%
  filter(dsstdat >= '2020-03-01' & dsstdat <= today_date + 1) %>% 
  group_by(dsstdat) %>% 
  summarise(n = n()) %>% 
  arrange(dsstdat) %>% 
  mutate(cumulative_recruitment = cumsum(n),
         country = 'UK')

rr_by_country = topline %>% 
  filter(!is.na(country)) %>%
  filter(dsstdat >= '2020-03-01' & dsstdat <= today_date + 1) %>% 
  group_by(country, dsstdat) %>% 
  summarise(n = n()) %>% 
  arrange(dsstdat) %>% 
  mutate(cumulative_recruitment = cumsum(n)) %>% 
  ggplot(aes(x = dsstdat, y = cumulative_recruitment)) + 
  geom_line(data = topline_by_country, aes(x = dsstdat, y = cumulative_recruitment, color = country), linetype = 'dashed')  + 
  geom_line(aes(colour = country)) + scale_color_lancet(name = 'Nation', breaks=c("UK","England", "Scotland","Wales")) + 
  theme_classic(14) + ylab('Cumulative Recruitment') + xlab('Enrollment Date')
rr_by_country
rm(topline_by_country,rr_by_country)
```
     
Row
-------------------------------------

### Last updated

```{r}
valueBox(lastrun %>% format("%H:%M %d-%m-%Y"), icon = "fa-calendar", color = '#8f8f8f')
```

### Number of patients (all tiers)

```{r}
valueBox(formatC(count(topline)$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#772ac3')
```

### Number of patients (Tier 0)

```{r}
valueBox(formatC(count(topline %>% filter(tiers_faorres___1 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

### Number of patients (Tier 1)

```{r}
valueBox(formatC(count(topline %>% filter(tiers_faorres___2 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

### Number of patients (Tier 2)

```{r}
valueBox(formatC(count(topline %>% filter(tiers_faorres___3 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

Row
-------------------------------------

### Demographics forms complete

```{r}
gauge(round(count(topline %>% filter(demographics_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))

```

### Onset / admission forms complete

```{r}
gauge(round(count(topline %>% filter(onset_and_admission_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Signs / symptoms forms complete

```{r}
gauge(round(count(topline %>% filter(admission_signs_and_symptoms_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Comorbidities forms complete

```{r}
gauge(round(count(topline %>% filter(comorbidities_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Outcomes / Complications (4 week lag)

```{r}
gauge(round(count(topline_outcomes_28 %>% filter(complications_complete == 'Complete' & outcome_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline_28 %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### About Us

Created by [Tom Drake](mailto:t.drake@ed.ac.uk), [SurgicalInformatics Group](https://surgicalinformatics.org/) at the [University of Edinburgh](https://ed.ac.uk/) as part of ISARIC-4C.


Scotland
=====================================
    
Row {.tabset .tabset-fade}
-------------------------------------

### Chart: Patients in ISARIC 4C-UK (at time of last update)

```{r, fig.width = 12}
scot_pts_by_hb = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'Scotland') %>%
  group_by(ccg_name) %>%
  summarise(count_recruited = n()) %>%
  ggplot(aes(x = reorder(ccg_name, -count_recruited), y = count_recruited, label = count_recruited)) + geom_bar(aes(fill = ccg_name), width = 0.5, stat = 'identity') +
  xlab('Health Board') + geom_label() + scale_fill_lancet(name = 'Health Board') + theme_classic(14) + ylab('Number of Patients') + theme(axis.text.x = element_blank())

scot_pts_by_hb

rm(scot_pts_by_hb)
```

### Chart: Recruitment rate by Health Board

```{r, fig.width = 12}
recruit_scotland = topline %>%
  filter(country == 'Scotland') %>%
  filter(!is.na(country)) %>%
  filter(dsstdat >= '2020-01-30' & dsstdat <= today() + 1) %>%
  group_by(dsstdat) %>%
  summarise(n = n()) %>%
  arrange(dsstdat) %>%
  mutate(cumulative_recruitment = cumsum(n),
         country = 'Scotland')

topline %>%
  filter(country == 'Scotland') %>%
  distinct(ccg_name) -> names_hb

rr_by_hb_scot = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'Scotland') %>%
  filter(dsstdat >= '2020-01-30' & dsstdat <= today() + 1) %>%
  group_by(ccg_name, dsstdat) %>%
  summarise(n = n()) %>%
  arrange(dsstdat) %>%
  mutate(cumulative_recruitment = cumsum(n)) %>%
  ggplot(aes(x = dsstdat, y = cumulative_recruitment)) +
  geom_line(data = recruit_scotland, aes(x = dsstdat, y = cumulative_recruitment, color = country), linetype = 'dashed')  +
  geom_line(aes(colour = ccg_name)) + scale_color_lancet(name = 'Health Board', breaks=c("Scotland", names_hb$ccg_name)) +
  theme_classic(14) + ylab('Cumulative Recruitment') + xlab('Enrollment Date')

rr_by_hb_scot

rm(recruit_scotland, rr_by_hb_scot, names_hb)
```

### Chart: Patients in ISARIC 4C-UK by Tier (at time of last update)

```{r, fig.width = 12, fig.height= 6}
tier_scotland_plot = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'Scotland') %>%
  group_by(ccg_name, tier_entered) %>%
  summarise(count_recruited = n()) %>%
  ggplot(aes(x = reorder(ccg_name, -count_recruited), y = count_recruited, label = count_recruited)) + geom_bar(aes(fill = ccg_name), width = 0.5, stat = 'identity') +
  xlab('Health Board') + geom_label() + scale_fill_lancet(name = 'Health Board') + theme_classic(14) + ylab('Number of Patients') + theme(axis.text.x = element_blank()) + facet_wrap(~tier_entered)

tier_scotland_plot

rm(tier_scotland_plot)
```   
   
### Table: Recruitment by Health Board
```{r}
tab_scot_hb = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'Scotland')%>% 
  mutate(place_name = as.character(place_name),
         city = as.character(city),
         ccg_name = as.character(ccg_name)) %>% 
  group_by(ccg_name, place_name, tier_entered, .drop = FALSE) %>% 
  summarise(number_recruited = n()) %>% 
  group_by(ccg_name) %>% 
  mutate(percentage_of_hb = paste0(sprintf("%.1f", round(number_recruited/sum(number_recruited) * 100, digits = 1)), '%')) %>% 
  rename('Health Board' = ccg_name,
         'Hospital' = place_name,
         'Tier' = tier_entered,
         'Number recruited' = number_recruited,
         'Percentage within Health Board' = percentage_of_hb) %>% 
   DT::datatable(options = list(bPaginate = FALSE ),
    rownames= FALSE)

tab_scot_hb

rm(tab_scot_hb)
```
     
Row
-------------------------------------

### Last updated

```{r}
valueBox(lastrun %>% format("%H:%M %d-%m-%Y"), icon = "fa-calendar", color = '#8f8f8f')
```

### Number of patients (all tiers)

```{r}
valueBox(formatC(count(topline %>% filter(country == 'Scotland'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#772ac3')
```

### Number of patients (Tier 0)

```{r}
valueBox(formatC(count(topline %>% filter(country == 'Scotland') %>% filter(tiers_faorres___1 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

### Number of patients (Tier 1)

```{r}
valueBox(formatC(count(topline %>% filter(country == 'Scotland') %>% filter(tiers_faorres___2 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

### Number of patients (Tier 2)

```{r}
valueBox(formatC(count(topline%>% filter(country == 'Scotland') %>% filter(tiers_faorres___3 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

Row
-------------------------------------

### Demographics forms complete

```{r}
gauge(round(count(topline%>% filter(country == 'Scotland') %>% filter(demographics_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'Scotland') %>%   
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Onset / admission forms complete

```{r}

gauge(round(count(topline %>% filter(country == 'Scotland') %>% filter(onset_and_admission_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'Scotland') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Signs / symptoms forms complete

```{r}
gauge(round(count(topline %>% filter(country == 'Scotland') %>% filter(admission_signs_and_symptoms_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'Scotland') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Comorbidities forms complete

```{r}
gauge(round(count(topline %>% filter(country == 'Scotland') %>% filter(comorbidities_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'Scotland') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Complications complete (4 week lag)

```{r}
gauge(round(count(topline_outcomes_28 %>% filter(country == 'Scotland') %>% filter(complications_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline_28 %>% filter(country == 'Scotland') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Outcomes forms complete (4 week lag)

```{r}
gauge(round(count(topline_outcomes_28 %>% filter(country == 'Scotland') %>% filter(outcome_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline_28 %>% filter(country == 'Scotland') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```


England
=====================================
    
Row {.tabset .tabset-fade}
-------------------------------------

### Chart: Patients in ISARIC 4C-UK by Tier (at time of last update)
```{r, fig.width = 12}
eng_pts_by_tier = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'England') %>%
  group_by(tier_entered) %>%
  summarise(count_recruited = n()) %>% 
  arrange(desc(count_recruited)) %>% 
  slice(1:20) %>% 
  ggplot(aes(x = reorder(tier_entered, -count_recruited), y = count_recruited, label = count_recruited)) + geom_bar(aes(fill = tier_entered), width = 0.5, stat = 'identity') +
  xlab('Tier') + geom_label() + scale_fill_lancet(name = 'Tier') + theme_classic(14) + ylab('Number of Patients')

eng_pts_by_tier

rm(eng_pts_by_tier)
```

### Chart: Top recruiting centres in England

```{r, fig.width = 12}
top_recruiting_eng = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'England') %>%
  group_by(place_name) %>%
  summarise(count_recruited = n()) %>% 
  arrange(desc(count_recruited)) %>% 
  slice(1:20) %>% 
  ggplot(aes(x = reorder(place_name, -count_recruited), y = count_recruited, label = count_recruited)) + geom_bar(aes(fill = place_name), width = 0.5, stat = 'identity') +
  xlab('Hospital') + geom_label() + scale_fill_discrete(name = 'Hospital') + theme_classic(14) + ylab('Number of Patients') + theme(axis.text.x = element_blank())

top_recruiting_eng

rm(top_recruiting_eng)
```

### Chart: Recruitment rate by Tier

```{r, fig.width = 12}

rr_eng_by_tier = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'England') %>%
  filter(tier_entered != 'Missing') %>%
  filter(dsstdat >= '2020-01-30' & dsstdat <= today() + 1) %>%
  group_by(tier_entered, dsstdat) %>%
  summarise(n = n()) %>%
  arrange(dsstdat) %>%
  mutate(cumulative_recruitment = cumsum(n)) %>%
  ggplot(aes(x = dsstdat, y = cumulative_recruitment)) +
  geom_line(aes(colour = tier_entered)) + scale_color_lancet(name = 'Tier') +
  theme_classic(14) + ylab('Cumulative Recruitment') + xlab('Enrollment Date')

rr_eng_by_tier

rm(rr_eng_by_tier)
```

### Table: Recruitment by Hospital

```{r}
tab_england = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'England') %>%
  mutate(place_name = as.character(place_name),
         city = as.character(city),
         ccg_name = as.character(ccg_name)) %>%
  group_by(city, place_name, tier_entered, .drop = FALSE) %>% 
  summarise(number_recruited = n()) %>% 
  group_by(place_name) %>% 
  mutate(percentage_of_hb = paste0(sprintf("%.1f", round(number_recruited/sum(number_recruited) * 100, digits = 1)), '%')) %>% 
  rename('City Region' = city,
         'Hospital' = place_name,
         'Tier' = tier_entered,
         'Number recruited' = number_recruited,
         'Percentage within Hospital' = percentage_of_hb) %>% 
      DT::datatable(options = list(bPaginate = FALSE ),
          rownames= FALSE)

tab_england

rm(tab_england)
```
     
Row
-------------------------------------

### Last updated

```{r}
valueBox(lastrun %>% format("%H:%M %d-%m-%Y"), icon = "fa-calendar", color = '#8f8f8f')
```

### Number of patients (all tiers)

```{r}
valueBox(formatC(count(topline %>% filter(country == 'England'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#772ac3')
```

### Number of patients (Tier 0)

```{r}
valueBox(formatC(count(topline %>% filter(country == 'England') %>% filter(tiers_faorres___1 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

### Number of patients (Tier 1)

```{r}
valueBox(formatC(count(topline %>% filter(country == 'England') %>% filter(tiers_faorres___2 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

### Number of patients (Tier 2)

```{r}
valueBox(formatC(count(topline%>% filter(country == 'England') %>% filter(tiers_faorres___3 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

Row
-------------------------------------

### Demographics forms complete

```{r}
gauge(round(count(topline%>% filter(country == 'England') %>% filter(demographics_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'England') %>%   
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))

```

### Onset / admission forms complete

```{r}

gauge(round(count(topline %>% filter(country == 'England') %>% filter(onset_and_admission_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'England') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Signs / symptoms forms complete

```{r}
gauge(round(count(topline %>% filter(country == 'England') %>% filter(admission_signs_and_symptoms_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'England') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Comorbidities forms complete

```{r}
gauge(round(count(topline %>% filter(country == 'England') %>% filter(comorbidities_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'England') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Complications complete (4 week lag)

```{r}
gauge(round(count(topline_outcomes_28 %>% filter(country == 'England') %>% filter(complications_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline_28 %>% filter(country == 'England') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Outcomes forms complete (4 week lag)

```{r}
gauge(round(count(topline_outcomes_28 %>% filter(country == 'England') %>% filter(outcome_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline_28 %>% filter(country == 'England') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```


Wales
=====================================
    
Row {.tabset .tabset-fade}
-------------------------------------

### Chart: Patients in ISARIC 4C-UK (at time of last update)

```{r, fig.width = 12}
pts_in_wales = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'Wales') %>%
  group_by(place_name) %>%
  summarise(count_recruited = n()) %>%
  ggplot(aes(x = reorder(place_name, -count_recruited), y = count_recruited, label = count_recruited)) + geom_bar(aes(fill = place_name), width = 0.5, stat = 'identity') +
  xlab('Health Board') + geom_label() + scale_fill_discrete(name = 'Hospital') + theme_classic(14) + ylab('Number of Patients') + theme(axis.text.x = element_blank())

pts_in_wales

rm(pts_in_wales)
```

### Chart: Recruitment rate by Health Board

```{r, fig.width = 12}
recruit_Wales = topline %>%
  filter(country == 'Wales') %>%
  filter(!is.na(country)) %>%
  filter(dsstdat >= '2020-01-30' & dsstdat <= today() + 1) %>%
  group_by(dsstdat) %>%
  summarise(n = n()) %>%
  arrange(dsstdat) %>%
  mutate(cumulative_recruitment = cumsum(n),
         country = 'Wales')

topline %>%
  filter(country == 'Wales') %>%
  distinct(place_name) -> names_hb

wales_rr_plot = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'Wales') %>%
  filter(dsstdat >= '2020-01-30' & dsstdat <= today() + 1) %>%
  group_by(place_name, dsstdat) %>%
  summarise(n = n()) %>%
  arrange(dsstdat) %>%
  mutate(cumulative_recruitment = cumsum(n)) %>%
  ggplot(aes(x = dsstdat, y = cumulative_recruitment)) +
  geom_line(data = recruit_Wales, aes(x = dsstdat, y = cumulative_recruitment, color = country), linetype = 'dashed')  +
  geom_line(aes(colour = place_name)) + scale_color_discrete(name = 'Hospital', breaks=c("Wales", names_hb$place_name)) +
  theme_classic(14) + ylab('Cumulative Recruitment') + xlab('Enrollment Date')

wales_rr_plot

rm(recruit_Wales, names_hb, wales_rr_plot)
```

### Chart: Patients in ISARIC 4C-UK by Tier (at time of last update)

```{r, fig.width = 13, fig.height= 6}
tier_pts_wales = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'Wales') %>%
  group_by(place_name, tier_entered) %>%
  summarise(count_recruited = n()) %>%
  ggplot(aes(x = reorder(place_name, -count_recruited), y = count_recruited, label = count_recruited)) + geom_bar(aes(fill = place_name), width = 0.5, stat = 'identity') +
  xlab('Health Board') + geom_label(nudge_x = 0.5) + scale_fill_discrete(name = 'Hospital') + theme_classic(14) + ylab('Number of Patients') + theme(axis.text.x = element_blank()) + facet_wrap(~tier_entered)

tier_pts_wales

rm(tier_pts_wales)
```   
   
### Table: Recruitment by Health Board
```{r}
tab_wales = topline %>%
  filter(!is.na(country)) %>%
  filter(country == 'Wales') %>%
  mutate(place_name = as.character(place_name),
         city = as.character(city),
         ccg_name = as.character(ccg_name)) %>%
  group_by(ccg_name, place_name, tier_entered, .drop = FALSE) %>% 
  summarise(number_recruited = n()) %>% 
  group_by(ccg_name) %>% 
  mutate(percentage_of_hb = paste0(sprintf("%.1f", round(number_recruited/sum(number_recruited) * 100, digits = 1)), '%')) %>% 
  rename('Health Board' = ccg_name,
         'Hospital' = place_name,
         'Tier' = tier_entered,
         'Number recruited' = number_recruited,
         'Percentage within Health Board' = percentage_of_hb) %>% 
   DT::datatable(options = list(bPaginate = FALSE ),
    rownames= FALSE)

tab_wales

rm(tab_wales)
```
     
Row
-------------------------------------

### Last updated

```{r}
valueBox(lastrun %>% format("%H:%M %d-%m-%Y"), icon = "fa-calendar", color = '#8f8f8f')
```

### Number of patients (all tiers)

```{r}
valueBox(formatC(count(topline %>% filter(country == 'Wales'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#772ac3')
```

### Number of patients (Tier 0)

```{r}
valueBox(formatC(count(topline %>% filter(country == 'Wales') %>% filter(tiers_faorres___1 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

### Number of patients (Tier 1)

```{r}
valueBox(formatC(count(topline %>% filter(country == 'Wales') %>% filter(tiers_faorres___2 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

### Number of patients (Tier 2)

```{r}
valueBox(formatC(count(topline%>% filter(country == 'Wales') %>% filter(tiers_faorres___3 == 'Checked'))$n, format="f", big.mark=" ", digits=0), icon = "fa-users", color = '#06bd6c')
```

Row
-------------------------------------

### Demographics forms complete

```{r}
gauge(round(count(topline%>% filter(country == 'Wales') %>% filter(demographics_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'Wales') %>%   
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))

```

### Onset / admission forms complete

```{r}

gauge(round(count(topline %>% filter(country == 'Wales') %>% filter(onset_and_admission_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'Wales') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Signs / symptoms forms complete

```{r}
gauge(round(count(topline %>% filter(country == 'Wales') %>% filter(admission_signs_and_symptoms_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'Wales') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Comorbidities forms complete

```{r}
gauge(round(count(topline %>% filter(country == 'Wales') %>% filter(comorbidities_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline %>% filter(country == 'Wales') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Complications complete (4 week lag)

```{r}
gauge(round(count(topline_outcomes_28 %>% filter(country == 'Wales') %>% filter(complications_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline_28 %>% filter(country == 'Wales') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```

### Outcomes forms complete (4 week lag)

```{r}
gauge(round(count(topline_outcomes_28 %>% filter(country == 'Wales') %>% filter(outcome_complete == 'Complete') %>% 
              distinct(subjid, .keep_all = T))$n / count(topline_28 %>% filter(country == 'Wales') %>%  
                                                           distinct(subjid, .keep_all = T))$n*100, digits = 1), 
      min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(65.1, 79.99), danger = c(0, 65)
))
```


